\documentclass[11pt,a4paper]{article}

% ── Packages ──────────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage[expansion=false]{microtype}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

% ── Theorem environments ──────────────────────────────────────────────────
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% ── Title / Author ────────────────────────────────────────────────────────
\title{Grand Rosetta Table:\\
  Complete Classification of Polynomial Continued Fraction Families\\
  and the Dichotomy Principle}
\author{Papanokechi Nnaji}
\date{April 2026}

\begin{document}
\maketitle

\begin{abstract}
We present a complete classification of four polynomial continued fraction (PCF)
families discovered via a systematic search over quadratic--linear parameter
spaces.  All families share the structure $a_n = (k_0 + 2m\sigma)\,n - 2n^2$,
$b_n = \varepsilon + 3n$, and obey a universal Gamma-function ratio formula
$V(m)/V(m{-}1) = (m+\alpha)/(m+\beta)$.  A sharp dichotomy emerges:
when $\alpha - \beta \in \mathbb{Z}$ the Pochhammer symbol telescopes to a
polynomial, yielding purely rational values (\emph{T-type});
when $\alpha - \beta \in \mathbb{Z} + \tfrac{1}{2}$ the values are
transcendental shifts of the classical $S$-family involving $\sqrt\pi$
and the Gamma function.
All identities are verified to 550--2000 digits of precision via
high-precision backward evaluation and PSLQ integer-relation detection.
\end{abstract}

% ══════════════════════════════════════════════════════════════════════════
\section{Introduction}\label{sec:intro}
% ══════════════════════════════════════════════════════════════════════════

A \emph{polynomial continued fraction} (PCF) is an expression of the form
\begin{equation}\label{eq:pcf-def}
  V \;=\; b_0 + \cfrac{a_1}{b_1 + \cfrac{a_2}{b_2 + \cfrac{a_3}{\ddots}}}
\end{equation}
where $a_n$ and $b_n$ are polynomials in $n$.
When the limit exists, it often equals a closed-form combination
of classical constants.  The programme of systematically discovering
such identities was initiated by the Ramanujan Machine
project~\cite{raab2021ramanujan}, which used massively parallel search
to rediscover and extend formulas for $\pi$, $e$, and $\zeta(3)$.
Theoretical foundations connecting PCFs to hypergeometric functions
are developed in~\cite{aptekarev2007turan,borwein2004mathematics},
while the classical relationship between continued fractions and
Pad\'e approximants dates to Euler and Gauss~\cite{jones1980continued}.

The \emph{$S$-family}, defined by $a_n = -n(2n - 2m - 1)$ and $b_n = 3n+1$,
is a one-parameter family whose $m=0$ member yields the well-known
$S^{(0)} = 2/\pi$ (equivalent, via Euler's continued fraction theorem,
to the Wallis product~\cite{lange1999elementary}).
Its closed form is given by the Gauss summation of a ${}_2F_1$
hypergeometric series evaluated at unit argument:
\begin{equation}\label{eq:s-family}
  S^{(m)} \;=\; \frac{2\,\Gamma(m+1)}{\sqrt{\pi}\,\Gamma(m+\tfrac{1}{2})}\,.
\end{equation}
This identity, together with the inter-member ratio
$S^{(m)}/S^{(m-1)} = 2m/(2m-1)$, serves as the ``Rosetta Stone''
template for our search: we scan all quadratic~$a_n$, linear~$b_n$ families
over small integer coefficients and flag those whose consecutive members
have exact rational ratios, then classify the survivors.

In this paper we report the results of this systematic scan.
All four families found are completely classified in the
Grand Rosetta Table (Table~\ref{tab:rosetta}), and a sharp
\emph{Dichotomy Principle} (Theorem~\ref{thm:dichotomy}) is established
distinguishing rational from transcendental families by the
arithmetic nature of a single parameter.

% ══════════════════════════════════════════════════════════════════════════
\section{Setup and family parameterisation}\label{sec:setup}
% ══════════════════════════════════════════════════════════════════════════

We consider one-parameter families of PCFs of the form~\eqref{eq:pcf-def}
with
\begin{equation}\label{eq:family-param}
  a_n(m) = (k_0 + 2m\sigma)\,n - 2n^2, \qquad
  b_n = \varepsilon + 3n, \qquad
  b_0 \in \{1,2\},
\end{equation}
where $k_0 \in \mathbb{Z}$ is a constant offset,
$\sigma \in \{+1,-1\}$ controls the sign of the $m$-coupling,
and $\varepsilon \in \{1,2\}$ is the $b$-intercept.
The parameter $m$ ranges over the non-negative integers (and analytically
continues to half-integers and beyond).

The systematic search scans all $(k_0, \sigma, \varepsilon, b_0)$
with $|k_0| \leq 5$, evaluates each family at $m = 0,1,\dotsc,5$
to~60-digit precision via backward continued-fraction evaluation
(depth~$N = 5000$), and applies a \emph{Wallis check}: the consecutive
ratios $V(m)/V(m{-}1)$ are tested for exact rationality by searching
for $p/q$ with $q \leq 200$ matching to $>50$ digits.
Families passing this filter are promoted to full verification at
550--2000 digits.

The four families that survive are listed below with their
explicit parameters:

\begin{center}
\begin{tabular}{crrrccc}
\toprule
Family & $k_0$ & $\sigma$ & $\varepsilon$ & $b_0$ & $a_n(m)$ & $b_n$ \\
\midrule
1 & $-3$ & $-1$ & $2$ & $2$ & $-(2m{+}3)\,n - 2n^2$ & $3n+2$ \\
2 & $-1$ & $-1$ & $2$ & $2$ & $-(2m{+}1)\,n - 2n^2$ & $3n+2$ \\
3 & $+3$ & $+1$ & $1$ & $1$ & $(2m{+}3)\,n - 2n^2$  & $3n+1$ \\
4 & $+4$ & $+1$ & $1$ & $1$ & $(2m{+}4)\,n - 2n^2$  & $3n+1$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent
Families~1--2 have $b_0 = 2$ and $\sigma = -1$ (negative $m$-coupling);
Families~3--4 have $b_0 = 1$ and $\sigma = +1$ (positive $m$-coupling).
This structural split is the origin of the dichotomy.

% ══════════════════════════════════════════════════════════════════════════
\section{The Grand Rosetta Table}\label{sec:table}
% ══════════════════════════════════════════════════════════════════════════

For each family, the consecutive-member ratio takes the universal form
\begin{equation}\label{eq:ratio}
  \frac{V(m)}{V(m-1)} \;=\; \frac{m + \alpha}{m + \beta}
\end{equation}
for specific constants $\alpha,\beta$.
Iterating this recurrence from the base value $V(0)$ gives the
universal closed form
\begin{equation}\label{eq:universal}
  V(m) \;=\; V(0)\;\frac{\Gamma(m+\alpha+1)\;\Gamma(\beta+1)}
                         {\Gamma(\alpha+1)\;\Gamma(m+\beta+1)}\,.
\end{equation}
Table~\ref{tab:rosetta} collects the parameters $\alpha$, $\beta$,
the base value $V(0)$, and the closed form for all four families.
Every entry has been verified to at least 550~stable digits by
comparing the PCF value (backward evaluation at depth $N=5000$,
precision~600\,dp) against the right-hand side
of~\eqref{eq:universal}.

\begin{table}[ht]
\centering
\caption{Complete classification of Rosetta Stone PCF families.
The telescoping condition $\alpha - \beta \in \mathbb{Z}$ causes all
transcendental factors to cancel, yielding rational closed forms.}
\label{tab:rosetta}
\begin{tabular}{cccccccll}
\toprule
Fam & Label & $\alpha$ & $\beta$ & $\alpha{-}\beta$
    & $V(0)$ & Ratio & Closed Form & Type \\
\midrule
1 & $T^{(m+1)}$   & $\frac{3}{2}$ & $\frac{1}{2}$  & $1$
  & $3$            & $\dfrac{m+\frac{3}{2}}{m+\frac{1}{2}}$
  & $2m + 3$       & Telescoping \\[6pt]
2 & $T^{(m)}$     & $\frac{1}{2}$ & $-\frac{1}{2}$ & $1$
  & $1$            & $\dfrac{m+\frac{1}{2}}{m-\frac{1}{2}}$
  & $2m + 1$       & Telescoping \\[6pt]
3 & $S^{(m+1)}$   & $1$   & $\frac{1}{2}$  & $\frac{1}{2}$
  & $\dfrac{4}{\pi}$ & $\dfrac{m+1}{m+\frac{1}{2}}$
  & $\dfrac{2\,\Gamma(m+2)}{\sqrt{\pi}\,\Gamma(m+\frac{3}{2})}$
  & $S$-shift \\[6pt]
4 & $S^{(m+\frac{3}{2})}$ & $\frac{3}{2}$ & $1$    & $\frac{1}{2}$
  & $\dfrac{3}{2}$   & $\dfrac{m+\frac{3}{2}}{m+1}$
  & $\dfrac{2\,\Gamma(m+\frac{5}{2})}{\sqrt{\pi}\,\Gamma(m+2)}$
  & $S$-shift \\
\midrule
\multicolumn{9}{p{0.92\linewidth}}{\textbf{Experiment log (2026-04-09):} Fractional $\beta$ sweep over reduced $p/q$ with $1 \le q \le 12$, $|\beta| \le 3$, and $\gcd(p,q)=1$ (266 cases). The best cubic candidates reached $81.1{+}$ stable digits, but no PSLQ relation was found in the rational, $\Gamma(1/3)$, or $\Gamma(2/3)$ sectors; the $\Gamma(1/4)$ and $\Gamma(3/4)$ sectors remain under-resolved.} \\
\bottomrule
\end{tabular}
\end{table}

\begin{remark}[Base values]
Family~3 satisfies $V_3(0) = S^{(1)} = 4/\pi$, which follows from
the Wallis-product representation of the $S$-family
at $m=1$~\cite{lange1999elementary}.
Family~4 satisfies $V_4(0) = S^{(3/2)} = 3/2$; here the Gamma
functions in~\eqref{eq:s-family} evaluate to $\Gamma(5/2) = 3\sqrt\pi/4$
and $\Gamma(2) = 1$, giving $2 \cdot (3\sqrt\pi/4)/(\sqrt\pi \cdot 1) = 3/2$.
\end{remark}

% ══════════════════════════════════════════════════════════════════════════
\section{The Dichotomy Principle}\label{sec:dichotomy}
% ══════════════════════════════════════════════════════════════════════════

The central structural result is:

\begin{theorem}[Dichotomy Principle]\label{thm:dichotomy}
Let $\{V(m)\}_{m \geq 0}$ be a PCF family of the
form~\eqref{eq:family-param} whose consecutive-member ratio satisfies
\[
  \frac{V(m)}{V(m-1)} = \frac{m+\alpha}{m+\beta}
\]
for constants $\alpha, \beta$ with $\alpha \neq \beta$.  Then:
\begin{enumerate}
\item[\textup{(T)}]
  If\/ $\alpha - \beta \in \mathbb{Z}$, then $V(m) \in \mathbb{Q}$
  for all $m \in \mathbb{Z}_{\geq 0}$
  \textup{(}provided $V(0) \in \mathbb{Q}$\textup{)}.
\item[\textup{(S)}]
  If\/ $\alpha - \beta \in \mathbb{Z} + \tfrac{1}{2}$,
  then $V(m)$ lies in $\mathbb{Q} \cdot \pi^{-1}$ for $m$ of one parity
  and in $\mathbb{Q}$ for $m$ of the other, with the
  transcendental factor $\sqrt\pi$ present in~\eqref{eq:universal}.
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
From~\eqref{eq:universal}, the $m$-dependent factor is the ratio
\[
  R(m) \;=\; \frac{\Gamma(m + \alpha + 1)}{\Gamma(m + \beta + 1)}\,.
\]

\emph{Case}~(T): When $d \coloneqq \alpha - \beta \in \mathbb{Z}_{>0}$
(the case $d < 0$ is analogous), the Gamma ratio reduces to a
Pochhammer symbol:
\[
  R(m) = (m + \beta + 1)_d
       = \prod_{j=0}^{d-1}(m + \beta + 1 + j)\,,
\]
which is a polynomial in~$m$ with rational coefficients
(since $\beta \in \tfrac{1}{2}\mathbb{Z}$).
The prefactor $\Gamma(\beta+1)/\Gamma(\alpha+1)$ is likewise rational
when $d$ is a positive integer, because $\Gamma(\alpha+1)/\Gamma(\beta+1)$
is itself a Pochhammer with rational argument.
Hence $V(m) = V(0) \cdot [\text{rational}]$.

Concretely, for Family~1 ($\alpha = 3/2$, $\beta = 1/2$, $d=1$):
\[
  R(m) = m + \tfrac{3}{2}, \quad
  \frac{\Gamma(3/2)}{\Gamma(5/2)} = \frac{2}{3}, \quad
  V(m) = 3 \cdot \tfrac{2}{3}(m + \tfrac{3}{2}) = 2m + 3.
\]

\emph{Case}~(S): When $\alpha - \beta = k + \tfrac{1}{2}$
with $k \in \mathbb{Z}$, the Gamma ratio $R(m)$ still reduces to a
Pochhammer, but the prefactor
$\Gamma(\beta+1)/\Gamma(\alpha+1)$ involves
$\Gamma$ at half-integer vs.\ integer arguments.
By the Legendre duplication formula,
\[
  \Gamma\bigl(n + \tfrac{1}{2}\bigr) = \frac{(2n)!}{4^n\,n!}\,\sqrt\pi\,,
\]
so the ratio acquires an ineliminable factor of $\sqrt\pi$ (or $1/\sqrt\pi$).
This factor propagates through~\eqref{eq:universal};
at integer~$m$ the $\Gamma$-terms in $R(m)$ alternate between producing an
additional $\sqrt\pi$ and cancelling it, giving the parity pattern
$V(m) \in \mathbb{Q}$ versus $V(m) \in \mathbb{Q}/\pi$.

Concretely, for Family~4 ($\alpha = 3/2$, $\beta = 1$, $d = 1/2$):
\[
  V_4(m) = \frac{2\,\Gamma(m+\tfrac{5}{2})}{\sqrt\pi\;\Gamma(m+2)}\,,
\]
and PSLQ confirms $V_4 \cdot \sqrt\pi \cdot \Gamma(m+2)/\Gamma(m+\tfrac{5}{2}) = 2$
to 200~digits for all tested $m$~values~\cite{ferguson1999pslq}.
\end{proof}

\begin{corollary}\label{cor:half-int-m}
Evaluating the $S$-type families at half-integer~$m$ swaps
the transcendental content:
Family~$4$ yields $V_4(-\tfrac{1}{2}) = 4/\pi$,
$V_4(\tfrac{1}{2}) = 16/(3\pi)$, and
$V_4(\tfrac{3}{2}) = 32/(5\pi)$,
while integer~$m$ gives $V_4(0) = 3/2$, $V_4(1) = 15/8$, $V_4(2) = 35/16$.
\end{corollary}

The phase diagram in Figure~\ref{fig:dichotomy} visualises the
dichotomy: integer values of the gap $\alpha - \beta$ correspond
to rational (T-type) families, while half-integer gaps produce
transcendental (S-type) families.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    >=latex,
    every node/.style={font=\small},
    rational/.style={line width=2pt, blue!70!black},
    transcendental/.style={line width=1.4pt, dashed, red!70!black},
    fampoint/.style={circle, inner sep=2.2pt, fill},
    famlabel/.style={font=\footnotesize\bfseries, anchor=south west, inner sep=2pt},
]

% ── Coordinate scaling ──
\def\xscale{3.2}
\def\yscale{2.6}

% ── Background shading for zones ──
\fill[blue!6] (-0.4*\xscale, 0.75*\yscale) rectangle (2.6*\xscale, 1.25*\yscale);
\fill[blue!6] (-0.4*\xscale, 1.75*\yscale) rectangle (2.6*\xscale, 2.25*\yscale);
\fill[red!6]  (-0.4*\xscale, 0.25*\yscale) rectangle (2.6*\xscale, 0.75*\yscale);
\fill[red!6]  (-0.4*\xscale, 1.25*\yscale) rectangle (2.6*\xscale, 1.75*\yscale);

% ── Axes ──
\draw[->] (-0.5*\xscale, 0) -- (2.8*\xscale, 0)
    node[right, font=\normalsize] {Parameter~$(m)$};
\draw[->] (-0.4*\xscale, -0.15*\yscale) -- (-0.4*\xscale, 2.4*\yscale)
    node[above, font=\normalsize] {Gap~$(\alpha - \beta)$};

% ── Y-axis tick labels ──
\foreach \y/\lab in {0/$0$, 0.5/$\tfrac{1}{2}$, 1/$1$, 1.5/$\tfrac{3}{2}$, 2/$2$} {
    \draw (-0.4*\xscale - 3pt, \y*\yscale) -- (-0.4*\xscale + 3pt, \y*\yscale);
    \node[left, font=\small] at (-0.4*\xscale - 4pt, \y*\yscale) {\lab};
}

% ── X-axis tick labels ──
\foreach \x in {0, 1, 2} {
    \draw (\x*\xscale, -3pt) -- (\x*\xscale, 3pt);
    \node[below, font=\small] at (\x*\xscale, -5pt) {$\x$};
}

% ── Horizontal zone lines ──
\draw[rational] (-0.3*\xscale, 1*\yscale) -- (2.5*\xscale, 1*\yscale);
\draw[rational] (-0.3*\xscale, 2*\yscale) -- (2.5*\xscale, 2*\yscale);
\node[blue!70!black, font=\footnotesize, anchor=west]
    at (2.55*\xscale, 1*\yscale) {Rational ($T$-type)};
\node[blue!70!black, font=\footnotesize, anchor=west]
    at (2.55*\xscale, 2*\yscale) {Rational ($T$-type)};

\draw[transcendental] (-0.3*\xscale, 0.5*\yscale) -- (2.5*\xscale, 0.5*\yscale);
\draw[transcendental] (-0.3*\xscale, 1.5*\yscale) -- (2.5*\xscale, 1.5*\yscale);
\node[red!70!black, font=\footnotesize, anchor=west]
    at (2.55*\xscale, 0.5*\yscale) {Transcendental ($S$-type)};
\node[red!70!black, font=\footnotesize, anchor=west]
    at (2.55*\xscale, 1.5*\yscale) {Transcendental ($S$-type)};

% ── Family discovery points ──
\node[fampoint, blue!70!black] (F2) at (0*\xscale, 1*\yscale) {};
\node[famlabel, blue!70!black, anchor=north east]
    at ([xshift=-2pt, yshift=-1pt] F2) {Fam\,2: $T^{(m)}$};

\node[fampoint, blue!70!black] (F1) at (0.35*\xscale, 1*\yscale) {};
\node[famlabel, blue!70!black, anchor=south west]
    at ([xshift=2pt, yshift=1pt] F1) {Fam\,1: $T^{(m+1)}$};

\node[fampoint, red!70!black] (F3) at (1*\xscale, 0.5*\yscale) {};
\node[famlabel, red!70!black, anchor=south west]
    at ([xshift=2pt, yshift=1pt] F3) {Fam\,3: $S^{(m+1)}$};

\node[fampoint, red!70!black] (F4) at (1.5*\xscale, 0.5*\yscale) {};
\node[famlabel, red!70!black, anchor=north west]
    at ([xshift=2pt, yshift=-1pt] F4) {Fam\,4: $S^{(m+\frac{3}{2})}$};

% ── Dashed zero line ──
\draw[gray!40, thin] (-0.3*\xscale, 0) -- (2.5*\xscale, 0);

% ── Legend ──
\node[draw, rounded corners=3pt, fill=white, inner sep=5pt,
      font=\footnotesize, text width=5.8cm, align=center]
    at (1*\xscale, -0.65*\yscale)
    {$\alpha - \beta \in \mathbb{Z}$~\textcolor{blue!70!black}{\rule{0.5cm}{1.5pt}}~Rational
     \quad$|$\quad
     $\alpha - \beta \in \mathbb{Z}{+}\tfrac{1}{2}$~{\color{red!70!black}\leaders\hbox{\kern1pt.\kern1pt}\hskip0.5cm\relax}~Transcendental};

\end{tikzpicture}
\caption{Phase diagram of PCF convergence types in the
$(\alpha{-}\beta,\, m)$ plane.
Rational solutions coalesce on integer gaps
($\alpha - \beta \in \mathbb{Z}$, solid blue),
while transcendental values emerge at half-integer shifts
($\alpha - \beta \in \mathbb{Z} + \tfrac{1}{2}$, dashed red).
Shaded bands indicate the predicted continuation of each zone
to higher gap values.}
\label{fig:dichotomy}
\end{figure}

% ══════════════════════════════════════════════════════════════════════════
\section{Connection to the $S$-family}\label{sec:s-family}
% ══════════════════════════════════════════════════════════════════════════

Families~3 and~4 are shifts of the classical $S$-family defined
in~\eqref{eq:s-family}.  Specifically:
\begin{itemize}
\item Family~3 satisfies $V_3(m) = S^{(m+1)}$, an integer shift.
  Its $a_n$ polynomial can be rewritten as
  $a_n = -n(2n - 2(m{+}1) - 1)$, which is the $S$-family
  at parameter $m' = m+1$.
\item Family~4 satisfies $V_4(m) = S^{(m+3/2)}$, a half-integer shift.
  Here $a_n = -n(2n - 2(m{+}\tfrac{3}{2}) - 1)$, which is the $S$-family
  at parameter $m' = m + 3/2$.
\end{itemize}
Both identities are confirmed by direct PCF-vs-PCF comparison
to 550~digits via the evaluation code accompanying this paper.

Families~1 and~2, by contrast, are \emph{not} shifts of the S-family:
they use $b_0 = 2$ and $b_n = 3n + 2$ (rather than $b_0 = 1$, $b_n = 3n+1$),
and the negative $m$-coupling ($\sigma = -1$) produces the integer gap
$\alpha - \beta = 1$ that triggers telescoping.
We denote these the \emph{$T$-type} families.

% ══════════════════════════════════════════════════════════════════════════
\section{Concluding remarks}\label{sec:conclusion}
% ══════════════════════════════════════════════════════════════════════════

\subsection{Open cubic PCF constant from the fractional-$\beta$ scan}

\begin{table}[ht]
\centering
\caption{Master summary table for currently open higher-degree PCF cases.}
\label{tab:open-master-summary}
\begin{tabular}{cccc}
\toprule
$(d,p,\alpha,\beta)$ & Value & Basis size & Verdict \\
\midrule
$(3,1,6,5/3)$ & $1.78856\ldots$ & $24$ & OPEN \\
\bottomrule
\end{tabular}
\end{table}

\input{dichotomy_d34_section.tex}

\subsection{Fractional $\beta$ sweep: negative result for $q \le 12$}

A dense follow-up sweep tested reduced fractions $\beta = p/q$ with
$1 \le q \le 12$, $|\beta| \le 3$, and $\gcd(p,q)=1$, giving
266 targeted cases across the cubic and quartic candidates singled out by
the earlier dichotomy search.  The strongest cubic cases,
$(3,1,6,8/3)$ and $(3,1,6,7/3)$, reached $81.1{+}$ and $80.9{+}$ stable
digits respectively, so the negative outcome is not attributable to a lack
of numerical stability at the current depth settings.

Despite this, no relation was detected in the rational,
$\Gamma(1/3)$, or $\Gamma(2/3)$ families at the $15$-digit PSLQ threshold.
This sweep therefore strengthens the evidence that the verified Rosetta
lines are concentrated on the integer and half-integer regimes already
represented in Table~\ref{tab:rosetta}.  What remains open is narrower:
the $\Gamma(1/4)$ and $\Gamma(3/4)$ buckets are still under-resolved
(they remained below $15$ stable digits), and genuinely new behaviour could
still emerge for finer fractional parameters with $q>12$.

The Dichotomy Principle provides a clean arithmetic criterion
for the nature of PCF limits within the quadratic--linear class
studied here.  Several directions remain:
\begin{itemize}
\item A fully rigorous proof (beyond the sketch in
  Theorem~\ref{thm:dichotomy}) via Euler's continued fraction
  theorem and Gauss summation of ${}_2F_1(a,b;c;1)$.
\item Extension to cubic $a_n$ or quadratic $b_n$, where the ratio
  structure may involve ${}_3F_2$ hypergeometric functions.
\item Lean~4 formalisation of the telescoping identities.
\end{itemize}

All computational verification code (PCF evaluators, PSLQ pipelines,
and the systematic search engine) is available at the
repository accompanying this manuscript.

% ══════════════════════════════════════════════════════════════════════════
% REFERENCES
% ══════════════════════════════════════════════════════════════════════════
\begin{thebibliography}{9}

\bibitem{raab2021ramanujan}
G.~Raayoni, S.~Gottlieb, Y.~Manor, G.~Pisha, Y.~Harris, U.~Mendlovic,
D.~Haviv, Y.~Hadad, and I.~Kaminer,
\emph{Generating conjectures on fundamental constants with the
Ramanujan Machine},
Nature \textbf{590} (2021), 67--73.

\bibitem{borwein2004mathematics}
J.~M.~Borwein and D.~H.~Bailey,
\emph{Mathematics by Experiment: Plausible Reasoning in the 21st Century},
A~K~Peters, 2004.

\bibitem{aptekarev2007turan}
A.~I.~Aptekarev, A.~Branquinho, and W.~Van~Assche,
\emph{Multiple orthogonal polynomials for classical weights},
Trans.\ Amer.\ Math.\ Soc.\ \textbf{355} (2003), 3887--3914.

\bibitem{jones1980continued}
W.~B.~Jones and W.~J.~Thron,
\emph{Continued Fractions: Analytic Theory and Applications},
Encyclopedia of Mathematics and its Applications, vol.~11,
Addison-Wesley, 1980.

\bibitem{lange1999elementary}
L.~J.~Lange,
\emph{An elegant continued fraction for~$\pi$},
Amer.\ Math.\ Monthly \textbf{106} (1999), 456--458.

\bibitem{ferguson1999pslq}
H.~R.~P.~Ferguson, D.~H.~Bailey, and S.~Arwade,
\emph{Recognition of algebraic and other constants using PSLQ},
Math.\ Comp.\ \textbf{68} (1999), 351--369.

\end{thebibliography}

\end{document}
