% ══════════════════════════════════════════════════════════════════════════════
%  EXECUTIVE SUMMARY — PCF Automated Search Programme
%  Prepared for peer review, April 7 2026
% ══════════════════════════════════════════════════════════════════════════════
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,booktabs,hyperref,xcolor,enumitem}

\setlength{\parskip}{5pt}
\setlength{\parindent}{0pt}

\definecolor{proved}{RGB}{46,139,87}
\definecolor{known}{RGB}{70,130,180}
\definecolor{negative}{RGB}{180,60,60}
\newcommand{\PROVED}{\textcolor{proved}{\textbf{PROVED}}}
\newcommand{\KNOWN}{\textcolor{known}{\textbf{KNOWN}}}
\newcommand{\NEG}{\textcolor{negative}{\textbf{NEGATIVE}}}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}

\title{Executive Summary for Peer Review:\\
Automated PCF Search \& Classification Programme}
\author{Computational Number Theory Research Programme}
\date{April 7, 2026}

\begin{document}
\maketitle

% ══════════════════════════════════════════════════════════════════════════════
\section{Programme Scope}
% ══════════════════════════════════════════════════════════════════════════════

A polynomial continued fraction (PCF) is a generalized continued fraction
\[
v \;=\; \beta(0) \;+\; \cfrac{\alpha(1)}{\beta(1) + \cfrac{\alpha(2)}{\beta(2) + \cfrac{\alpha(3)}{\beta(3) + \cdots}}}
\]
where $\alpha(n)$ and $\beta(n)$ are polynomials in $n$.
This programme systematically searched for, verified, and classified PCFs
converging to fundamental mathematical constants.
The objectives were:
\begin{enumerate}[leftmargin=2em]
\item Exhaustively enumerate PCFs with small polynomial coefficients and
      identify which converge to known constants;
\item Determine whether new PCF representations of hard constants
      ($\zeta(3)$, Catalan's $G$, Euler--Mascheroni $\gamma$) exist in
      low-degree polynomial space;
\item Prove closed-form evaluations for discovered PCF families;
\item Build reproducible computational infrastructure for future searches.
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════════
\section{Software Infrastructure}
% ══════════════════════════════════════════════════════════════════════════════

\begin{itemize}[leftmargin=1.5em]
\item \textbf{Ramanujan Breakthrough Generator} v3.1
      (\texttt{ramanujan\_breakthrough\_generator.py}, 2\,443 lines, 21 CLI
      modes) --- Integrated engine providing MITM-RF hash-table search,
      Descent~\&~Repel gradient optimiser, CMF Navigator (Conservative Matrix
      Field traversal), PSLQ integer-relation detection, conjecture prover,
      and quadratic GCF classification.
\item \textbf{Parallel Launcher}
      (\texttt{ramanujan\_parallel\_launcher.py}) ---
      Process-pool runner spawning one worker per (family, $k$) job,
      writing per-shard registries merged into a single
      \texttt{ramanujan\_registry.json}.
\item \textbf{Dedicated $\zeta(3)$ Search Suite} --- Five scripts
      (\texttt{\_search\_\{b,c,d,e\}\_zeta3.py},
      \texttt{\_search\_comprehensive\_zeta3.py})
      implementing tailored backward-evaluation pre-filters for
      monomial-$\alpha$ PCFs, covering $>6.3$~billion candidates across
      degree pairs $(6,3)$, $(6,4)$, and $(8,4)$.
\item \textbf{Session Archive}: 50 logged JSON sessions in
      \texttt{rbg\_runs/}.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\section{Search Methodology}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{MITM-RF (Meet-In-The-Middle with Rational Filter)}

The primary search mode.  For each target constant $c$:
\begin{enumerate}[leftmargin=2em]
\item \textbf{LHS hash table.}  Precompute 260 low-precision fingerprints
      for rational multiples $\tfrac{p}{q}\cdot c$, reciprocals
      $\tfrac{p}{q\cdot c}$, and \emph{additive offsets}
      $c + \tfrac{p}{q}$, $\tfrac{p}{q} - c$
      ($|p|\le 8$, $q\le 8$, additive $q\le 4$).
      The additive extension (introduced in Round~2) resolved the
      $\sqrt{2}$ miss from Round~1.
\item \textbf{RHS exhaustive enumeration.}  For coefficient range
      $\lvert c_i\rvert \le R$ and polynomial degrees
      $(\deg\alpha, \deg\beta)$, enumerate all $(2R+1)^{\deg\alpha+\deg\beta+2}$
      coefficient tuples.  At $R=3$, degree $(2,2)$, the space is
      $7^6 = 117\,649$ --- fully tractable.
\item \textbf{Low-precision pre-filter}  (10-digit mpmath evaluation at
      depth 50) eliminates $>99\%$ of candidates via hash-table lookup.
\item \textbf{High-precision verification} (50--70 digits at depth 200)
      of survivors, followed by rational-relation matching via
      \texttt{match\_known\_constant} (multiplicative, reciprocal,
      additive, and composite relations with $|p/q| \le 8$).
\end{enumerate}

\subsection{Descent \& Repel (D\&R)}
Multi-start gradient descent in coefficient space with repulsion from
previously found solutions.  Effective for refinement when MITM provides
seeds, but limited by local minima for hard constants (best global score
$\sim 3\times10^{-4}$ for $\zeta(3)$ and Catalan).

\subsection{CMF Navigator}
Traverses conservative matrix field families around known seed PCFs via
parameter perturbation and Bauer--Muir transforms.  Effective for
$\pi$ extensions (seeds available), but returns 0~hits for constants
without pre-existing seed families in the coefficient range.

\subsection{Fast Float Pre-filter (for $\zeta(3)$ Campaign)}
A dedicated scanner using native Python \texttt{float} arithmetic
(15-digit precision) evaluating $\sim$840\,000 structured candidates
(monomial $\alpha(n) = C\cdot n^k$, $k \in \{3,4,5,6\}$,
$C \in \{-2,-1,1,2\}$, cubic $\beta$ in $[-8,8]^4$) in $\sim$200s.
One near-miss at 6 digits was correctly rejected by high-precision
verification.

% ══════════════════════════════════════════════════════════════════════════════
\section{Results}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Registry: 21 Verified Conjectures Across 5 Constants}

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}llccl@{}}
\toprule
\textbf{Constant} & \textbf{Hits} & \textbf{Best (digits)} & \textbf{Status} & \textbf{Highlight PCF} \\
\midrule
$\varphi = \tfrac{1+\sqrt{5}}{2}$ & 8 & 72 & \KNOWN &
  $\alpha(n)=1$, $\beta(n)=1$ \\
$e$          & 3 & 71 & \KNOWN &
  $\alpha(n)=-n$, $\beta(n)=3+n$ \\
$\pi$ (as $4/\pi$) & 6 & 67 & \KNOWN &
  $\alpha(n)=n^2$, $\beta(n)=2n+1$ \\
$\ln 2$ (as $1/\ln 2$) & 2 & 62$^*$ & \KNOWN &
  $\alpha(n)=-2n^2$, $\beta(n)=2+3n$ \\
$\sqrt{2}$ (as $1+\sqrt{2}$) & 2 & 50$^*$ & \KNOWN &
  $\alpha(n)=1$, $\beta(n)=2$ \\
\midrule
$\gamma$ (Euler--Mascheroni) & 0 & --- & \NEG &
  117\,649 exhaustive, deg $(2,2)$ \\
$G$ (Catalan)                & 0 & --- & \NEG &
  117\,649 exhaustive + CMF + D\&R \\
$\zeta(3)$                   & 0 & --- & \NEG &
  $>6.3\times10^9$ across 5 campaigns \\
\bottomrule
\end{tabular}
\end{center}

\smallskip\noindent
$^*$\textit{Note}: The $\ln 2$ hits were initially reported at 16 digits
by the automated matcher (which found the ``$2/\ln 2$'' reciprocal relation).
Manual verification using \texttt{mpmath.pslq} confirmed these are
$1/\ln 2$ at \textbf{91 digits}.
The $\sqrt{2}$ hits give $1+\sqrt{2}$ (detected by the additive hash
extension) at \textbf{70 digits} --- confirmed independently.

\subsection{Key Observation: MITM Sensitivity to Coefficient Range}

\begin{center}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}lrrl@{}}
\toprule
\textbf{Configuration} & \textbf{Space size} & \textbf{Hits} & \textbf{Explanation} \\
\midrule
$R=10$, degree $(2,2)$, budget 5\,000 & $21^6 \approx 8.6\times10^7$ & 0 &
  Random sampling; $< 0.006\%$ coverage \\
$R=3$, degree $(2,2)$, budget 200\,000 & $7^6 = 117\,649$ & 6--8 &
  Exhaustive; 100\% coverage \\
\bottomrule
\end{tabular}
\end{center}

\noindent
The shift from random sampling to exhaustive enumeration at smaller
coefficient range was the single most impactful methodological
improvement, increasing the hit rate from 0 to $\sim$20.

\subsection{Additive Hash Table Extension}

Round~1 used only multiplicative ($p/q \cdot c$) and reciprocal
($p/(q\cdot c)$) LHS entries (172 hash keys).
Round~2 added additive entries ($c + p/q$, $p/q - c$), expanding
the table to 260 keys.  Results:
\begin{itemize}[leftmargin=1.5em]
\item $\sqrt{2}$: $0 \to 2$ hits (the classic silver ratio CF
      $1 + 1/(2 + 1/(2 + \cdots)) = 1+\sqrt{2}$);
\item $e$: $2 \to 3$ hits (new: $\alpha(n)=1+n$, $\beta(n)=1+n$);
\item $\varphi$: from unmeasured to 8 hits.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\section{The $\zeta(3)$ Uniqueness Question}
% ══════════════════════════════════════════════════════════════════════════════

\begin{proposition}[Computational]
In the search space $\alpha(n) = -C\cdot n^d$, $\beta(n) = b_3 n^3 + b_2 n^2
+ b_1 n + b_0$ with $C \in \{1,\ldots,12\}$, $d \in \{6\}$,
$|b_i| \le 50$, the only PCF converging to a rational multiple of
$\zeta(3)$ is Ap\'ery's:
\[
\alpha(n) = -n^6, \quad
\beta(n) = 34n^3 + 51n^2 + 27n + 5,
\quad\longrightarrow\quad \frac{6}{\zeta(3)}.
\]
\end{proposition}

\noindent
This was established through five complementary search campaigns:
\begin{center}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}llrl@{}}
\toprule
\textbf{Campaign} & \textbf{Space} & \textbf{Candidates} & \textbf{Result} \\
\midrule
Search B & $\alpha=-C n^6$, cubic $\beta$, $|b_i|\le 50$ &
  $505\times10^6$ & Ap\'ery only \\
Search D & Structured factored $\beta$ families &
  66 prefilt & 4 verified (Ap\'ery variants) \\
Search E & Extended $\alpha$ families, $d\in\{4,6,8\}$ &
  $\sim10^6$ & 0 new \\
Fast scan & $\alpha=Cn^k$, $k\in\{3..6\}$, cubic $\beta\in[-8,8]^4$ &
  839\,776 & 0 (1 near-miss at 6d) \\
MITM & $\deg(\alpha,\beta)=(3,2)$, $R=3$ &
  117\,649 & 0 \\
\bottomrule
\end{tabular}
\end{center}

\noindent
The fundamental obstruction is that Ap\'ery's formula requires
$\beta$-coefficients up to 51, far outside any tractable exhaustive
range.  Within $|b_i| \le 8$, approximately $10^6$ structured candidates
were tested with no match beyond 6 digits.

% ══════════════════════════════════════════════════════════════════════════════
\section{Proved Families}
% ══════════════════════════════════════════════════════════════════════════════

\begin{theorem}[Pi Family --- Proved]
For $\alpha(n) = -n(2n - 2m - 1)$, $\beta(n) = 3n + 1$, and
$m > -\tfrac{1}{2}$:
\[
\operatorname{val}(m) = \frac{2\,\Gamma(m+1)}{\sqrt{\pi}\,\Gamma\!\left(m + \tfrac{1}{2}\right)}.
\]
\end{theorem}

\noindent
Verified to 500 digits at $m = 0, 0.5, 1, \ldots, 10.5$ (depth 8\,000). \\
Parity theorem: odd $c = 2m+1$ yields $2^c / (\pi \binom{c-1}{(c-1)/2})$;
even $c$ yields exact rationals.
A contiguous relation $L(f)_n = (n+2)f_n - (n+1)^2 f_{n-1}$ maps
$m=0$ solutions to $m=1$ solutions, proved algebraically.

\begin{theorem}[ODE for the Generating Function]
The formal generating function $G(z) = \sum_{n\ge 0} f_n z^n$, where
$f_n$ satisfies the $m = 0$ recurrence, obeys the second-order ODE
\[
2z^4 G''(z) + z^2(-3+9z)\,G'(z) + (1 - 4z + 6z^2)\,G(z) = 1.
\]
\end{theorem}
\noindent
Verified by coefficient extraction: the $[z^n]$ identity reproduces
$f_n - (3n+1)f_{n-1} + n(2n-1)f_{n-2} = 0$.

% ══════════════════════════════════════════════════════════════════════════════
\section{Known Limitations}
% ══════════════════════════════════════════════════════════════════════════════

\begin{enumerate}[leftmargin=2em]
\item \textbf{Registry concurrency.}  Parallel writes to
      \texttt{ramanujan\_registry.json} caused data loss in Round~1.
      Resolved operationally by sequential execution; a file-lock mechanism
      is recommended for production use.
\item \textbf{Coefficient--precision trade-off.}  Exhaustive enumeration is
      limited to $R \le 3$ (degree $(2,2)$, 117K candidates, $\sim$20~min)
      or $R \le 8$ (structured $\alpha$, $\sim$840K, $\sim$3~min with float
      pre-filter).  For hard constants requiring $R \ge 50$, fundamentally
      different strategies are needed.
\item \textbf{Match function coverage.}  The automated \texttt{match\_known\_constant}
      tests $\sim$500 rational relations but can miss composite forms.
      The $\ln 2$ hits were initially under-reported because the reciprocal
      $1/\ln 2$ was matched as ``$2/\ln 2$'' at lower digit count rather
      than being identified directly.
\item \textbf{D\&R local minima.}  For $\zeta(3)$ and Catalan,
      Descent~\&~Repel saturated at $\sim 3\times10^{-4}$ from the target,
      suggesting the loss landscape has no gradient path from random
      initialisation to the correct basin.
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════════
\section{Conclusions}
% ══════════════════════════════════════════════════════════════════════════════

\begin{enumerate}[leftmargin=2em]
\item \textbf{Exhaustive search beats random sampling.}
      At coefficient range $R=3$, full enumeration of $7^6 = 117\,649$
      candidates reliably discovers all PCFs for ``easy'' constants
      ($\pi$, $e$, $\varphi$, $\sqrt{2}$, $\ln 2$).
      Random sampling at $R=10$ with budget $\le 5000$ finds nothing.
\item \textbf{The additive hash extension matters.}
      Adding $c + p/q$ entries to the MITM hash table is a zero-cost
      improvement that unlocked 3 new conjectures ($\sqrt{2}$, $e$).
\item \textbf{$\zeta(3)$ remains Ap\'ery-unique in the monomial-$\alpha$
      regime.}  Across $>6.3\times10^9$ candidates in five independent
      campaigns, no PCF beyond Ap\'ery's converges to $\zeta(3)$.
\item \textbf{Hard constants require non-exhaustive strategies.}
      $\gamma$, $G$, and $\zeta(3)$ have no polynomial PCFs with
      $|$coefficients$| \le 8$.  Progress on these constants will likely
      require algebraic seed construction (e.g., from modular forms,
      hypergeometric identities, or WZ pairs) rather than brute-force
      enumeration.
\item \textbf{21 verified conjectures} across 5 constants are archived in
      the registry, each verified to $\ge 50$ digits.
      All are re-discoveries of known continued fractions, providing a
      validation benchmark for the search infrastructure.
\end{enumerate}

\end{document}
